### 2020-03-10 defesa/presentation/slides.tex
wip

\usepackage{amsthm, amsfonts, amsmath, amssymb} % Pacote para a definicao dos ambientes matematicos
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[mathscr]{eucal}
\usepackage{tikz}
\usetikzlibrary{quotes, angles, intersections}
\newcommand{\R}{\mathbb{R}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\bigO}{\mathscr{O}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}

\author{Danilo Tedeschi\\Dra. Marina Andretta}
\title{Fixed-Shape Ellipse by Three Points}
\institute{Universidade de São Paulo}
\date{25 de Outubro de 2019}

@@

	\begin{frame}{Introduction}
		The shape of an ellipse is given by its major-axis and minor-axis, $(a, b) \in \mathbb{R}^2$, with $a > b > 0$.

@@

			%\caption{The ellipse as a parametric curve.}
			\input{ellipse_figure.tex}
			\label{fig:ellipse_params}
			\caption{An ellipse with shape parameters $a$ and $b$.}
		\end{figure}

@@

\begin{frame}{Introduction}
	Here, the shape will be fixed and the center and angle of rotation are free.

	\begin{figure}
	\centering

	%\caption{The ellipse as a parametric curve.}
	\includegraphics[scale=.5]{3ellipses.pdf}
	\label{fig:ell}
	\caption{A fix-shape ellipse at different centers and with different angles of rotation.}
	\end{figure}
\end{frame}

\begin{frame}{Introduction}{Problem definition}
Given three points $u, v, w \in \R^2$, and the shape $(a,b) \in \R^2$ of an ellipse:
	\begin{figure}
	\centering

	%\caption{The ellipse as a parametric curve.}
	\includegraphics[scale=.5]{e3psol1.pdf}
	\label{fig:e3psol1}
	\caption{An instance of the problem.}
\end{figure}
\end{frame}

\begin{frame}{Introduction}{Problem definition}
	A solution is given by the ellipse's center $q \in \R^2$ and the angle of rotation $\theta \in [0, \pi)$, such that $u, v, w$ lie on its border. \textbf{We want to find every solution!}
	\begin{figure}
		\centering

		%\caption{The ellipse as a parametric curve.}
		\includegraphics[scale=.5]{e3psol2.pdf}
		\label{fig:e3psol2}
		\caption{Every solution for the instance shown previously.}
	\end{figure}
\end{frame}

\begin{frame}{Introduction}
	The equation of an ellipse is given by:

	\begin{equation*}
	\frac{\left(\left[\begin{array}{c}
	x-q_x\\
	y-q_y
		\end{array}\right]^T
		\left[\begin{array}{c}
		\cos\theta\\
		\sin\theta
		\end{array}\right]
		\right)^2}{a^2}+\frac{\left(\left[\begin{array}{c}
		x-q_x\\
		q_y-y
		\end{array}\right]^T
		\left[\begin{array}{c}
		\sin\theta\\
		\cos\theta
		\end{array}\right]
		\right)^2}{b^2} = 1.
	\end{equation*}

	\begin{itemize}
		\item Fixing the points $u, v, w$, we get $3$ equations and $3$ unknowns $(q_x, q_y, \theta)$.
		\item Finding every solution is difficult.
	\end{itemize}
\end{frame}

\begin{frame}{Transforming the problem}
	Let's make the problem simpler by transforming it into a circle problem.

	An ellipse with shape $(a, b)$ can be transformed into a circle of radius $b$ through scaling the $x$-axis by $\frac{b}{a}$:
	\begin{figure}
		\centering

		%\caption{The ellipse as a parametric curve.}
		\includegraphics[scale=.5]{el1.pdf}
		\label{fig:el1}
		\caption{Turning an ellipse with shape $(a, b)$ into a circle of radius $b$.}
	\end{figure}

\begin{frame}{Transforming the problem}

	Let's rotate the points instead of rotating the ellipse:

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol1}
		\caption{Three points at their initial location.}
		\label{fig:sol1}
	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}

	Firstly, we rotate leaving one point fixed at $(0, 0)$:

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol2}
		\caption{After rotation.}
		\label{fig:sol2}
	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}

	Then, we scale by $\frac{b}{a}$ and check the radius of the circle:

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol3}
		\caption{After scaling by $\frac{b}{a}$.}
		\label{fig:sol33}
	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}
	Then, we apply the inverse transformation.

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol31}
		\caption{After scaling by $\frac{a}{b}$.}

	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}

	If the radius is $b$, the angle of rotation is a solution:

	\begin{figure}
		\centering
		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{sol4}
		\caption{A solution is obtained after scaling by $\frac{a}{b}$ and rotating by $-\theta$.}
		\label{fig:sol4}
	\end{figure}
\end{frame}

\begin{frame}{Transforming the problem}
	Formally, we can transform the problem by:

	\begin{itemize}
		\item Translate the points so $u=(0, 0)$.
		\item Rotate by $\theta$ and scale the $x$-axis by $\frac{b}{a}$.
		\item Find the $\theta$'s which produce a circle with radius $b$.
	\end{itemize}

	This transformation is expressed by:

	\begin{equation*}\label{eq:trpnts}
	\varphi(p, \theta)=\left[\begin{array}{cc}
	\frac{b}{a}&0\\
	0&1
	\end{array}\right]
	\left[\begin{array}{cc}
	\cos{\theta}&\sin{\theta}\\
	-\sin{\theta}&\cos{\theta}
	\end{array}\right]\left[\begin{array}{c}
	p_x\\
	p_y
	\end{array}\right],
	\end{equation*}
	for $p=u, v, w$.

	\textbf{This is an one variable problem on a closed interval!}

\begin{frame}{Fixed-shape ellipse by three points}
	There is a known formula for the radius of a circumscribed circle \cite[p.~189]{johnson1960}:

	\begin{equation*}
	R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)}
	\end{equation*}

	\begin{itemize}
		\item $R$ is the radius.
		\item $A(\theta)$ is the area of the triangle defined by the points $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
	\end{itemize}
	\vspace{\baselineskip}

\begin{frame}{Fixed-shape ellipse by three points}
We define the function $\xi : [0, \pi) \mapsto \R$:

	\begin{equation*}
	\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2
	\end{equation*}

	\begin{itemize}
		\item It can be written as 
		$$\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
		\item The roots of $\xi$ are solutions of our problem.	
\end{itemize}

\begin{frame}{Fixed-shape ellipse by three points}
	An example with no roots.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{036}
		\caption{An example of $\xi$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Fixed-shape ellipse by three points}
	An example with two roots.
\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.5]{012}
	\caption{Another example of $\xi$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

\begin{frame}{Fixed-shape ellipse by three points}
	An example with four roots.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{g4sol}
		\caption{An example of $\xi$ with $4$ roots.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Polynomial Interpolation}
	It is a way to approximate a function by a simpler one (a polynomial).

	\begin{itemize}
		\item A degree $n$ of the interpolation is determined.
		\item $n+1$ points are chosen, such that the polynomial has to pass through.
		\item Can be calculated using Lagrange's formula.

		\item We can find every root of a polynomial by determining the eigenvalues of a matrix called The Companion Matrix \cite[p.~195]{horn}.

		\item Depending on the points, the interpolation can be a bad approximation. It can get worse even if $n$ is increased (Runge's Phenomenon) \cite[p.~37]{powell}.
	\end{itemize}
\end{frame}

\begin{frame}{Chebyshev Interpolation}

	\begin{block}{Chebyshev Polynomial}
		$T_n: [-1, 1] \mapsto [-1, 1]$ is the $n$-degree Chebyshev polynomial \cite{chebbook}:
		\begin{equation*}
		T_n(\cos t) = \cos(nt)
		\end{equation*}
	\end{block}
	Also, it can be defined recursively:	
	\begin{align*}
	&T_0(x) = 1\\
	&T_1(x) = x\\
	&T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x)
	\end{align*}

\begin{frame}{Chebyshev Interpolation}
\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.6]{chebpoly}
	\caption{Chebyshev Polynomials of degree $1, 2, 3, 4$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

\begin{frame}{Chebyshev Interpolation}
	Interpolation on the roots of $T_n$, also known as Chebyshev Nodes:

	\begin{equation*}
		x_k = \cos\left(\pi\frac{2k - 1}{2n}\right)
	\end{equation*}

	The interpolation of a function $f : [-1, 1] \mapsto \R$ can be written directly using Chebyshev polynomial as basis:

	\begin{equation*}
	f(x) \approx \sum_{k=0}^{n} a_k T_k(x)
	\end{equation*}

	\begin{itemize}
		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
	\end{itemize}
\end{frame}

\begin{frame}{Chebyshev Interpolation}
		Why is it good?

	\begin{itemize}
		\item Numerically stable! Way better then polynomials in the power format \cite{gautschi:1979}.

		\item No Runge's Phenomenon, the interpolation converges to $f$.
		\begin{itemize}
			\item $\bigO(n^{-m})$ if $f$ is $m$ times differentiable \cite[p.~28]{gottlieb}.
			\item $\bigO(C^n)$, for $C<1$, if $f$ is analytical in a neighborhood of $[-1, 1]$ \cite{battles:2004}.
		\end{itemize}

		\item Very used in practice: 
		\begin{itemize}
			\item Present in external libraries like NumPy for Python.
			\item Matlab tool Chebfun: allows functions to be treated as vectors.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Example}
	$\xi$ and its approximation of degree $8$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{inexn8}
		\caption{An example of degree $8$ approximation.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Example}
	$\xi$ and its approximation of degree $10$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{inexn10}
		\caption{An example of degree $10$ approximation.}

	\end{figure}
\end{frame}

\begin{frame}{Example}
	$\xi$ and its approximation of degree $12$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{inexn12}
		\caption{An example of degree $12$ approximation.}

	\end{figure}
\end{frame}

\begin{frame}{Chebyshev Interpolation}
	Choosing the degree of the interpolation:

	\begin{itemize}
		\item There is no guaranteed way to choose it.
		\item A good rule is to examine the last coefficient (the last coefficient rule-of-thumb \cite[p~.50]{boyd:2001}).
		\item For a predefined $\epsilon$, choose $n$, such that:

		\begin{equation*}
		|a_n| \le \epsilon
		\end{equation*}

		\item There are other ways like checking the error on a Lobatto grid \cite{boyd:2007}.
	\end{itemize}
\end{frame}

\begin{frame}{Chebyshev Interpolation}
	For $n=32$, a precision of $10^{-10}$ is expected.

	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{error_coef}
		\caption{$|a_n|$ for the interpolation of $\xi$ for an instance.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Chebyshev Interpolation}{Roots}
	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$, we have:

	\begin{equation*}
	\left[\begin{array}{cccccc}
	0&1&0&0&0\\
	\frac{1}{2} & 0 & \frac{1}{2} & 0 & 0\\
	0 & \frac{1}{2} & 0 & \frac{1}{2} & 0\\
	0 & 0 & \frac{1}{2} & 0 & \frac{1}{2}\\
	-\frac{a_0}{2a_5} & -\frac{a_1}{2a_5} &-\frac{a_2}{2a_5} &-\frac{a_3}{2a_5} &-\frac{a_4}{2a_5}\\
	\end{array}\right]
	\end{equation*}

	\begin{itemize}
		\item This is a Hessenberg matrix.
		\item Its eigenvalues can be found by a QR decomposition in $\bigO(n^3)$.
	\end{itemize}
\end{frame}

\begin{frame}{Chebyshev Interpolation}{Roots}
	The largest error on roots that were found for $n=32$ is around $10^{-14}$ for an instance:
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{error_roots}
		\caption{$|\xi(\hat{\theta})|$, where $\hat{\theta}$ is a root of $f_n$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Chebyshev Interpolation}{Roots}
	The experiments were made using Python with the NumPy library. The running time is really low, even for $n=64$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{running_time}
		\caption{The running time to find the roots of $f_n$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Example}
	An example with $4$ solutions.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{e3psol012}
		\caption{An example with $4$ solutions.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}[allowframebreaks]
	\frametitle{References}
	\bibliographystyle{amsalpha}
	\bibliography{references}
\end{frame}

>>>>

\usepackage{amsthm, amsfonts, amsmath, amssymb} % Pacote para a definicao dos ambientes matematicos
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[mathscr]{eucal}
\usepackage{tikz}
\usetikzlibrary{quotes, angles, intersections}
\newcommand{\R}{\mathbb{R}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\Pp}{\mathscr{P}}
\newcommand{\bigO}{\mathscr{O}}
\newcommand{\Cc}{\mathscr{C}}
\newcommand{\E}{\mathscr{E}}
\newcommand{\F}{\mathscr{F}}
\newcommand{\Ww}{\mathscr{W}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\norm}[2][2]{\left\lVert#2\right\rVert_{#1}}

\author{Danilo Tedeschi\\Dra. Marina Andretta}
\title{Algorithms for Planar Maximum Covering Location by Ellipses Problems}
\institute{Universidade de São Paulo}
\date{25 de Outubro de 2019}

@@

\begin{frame}{Introduction}

	Two versions: 
	\begin{itemize}
		\item Planar Maximum Covering Location by Ellipses Problem (MCE) \cite{canbolat};
		\item Planar Maximum Covering Location by Ellipses with Rotation Problem (MCER) \cite{andreta}.
	\end{itemize}
\end{frame}

\begin{frame}{Introduction}{Ellipse}
	The shape of an ellipse is given by its major-axis and minor-axis, $(a, b) \in \mathbb{R}^2$, with $a > b > 0$.

@@

		%\caption{The ellipse as a parametric curve.}
		\includegraphics[scale=.3]{../tex/figures/rotated_ellipse.pdf}
		\label{fig:ellipse_params}
		\caption{An ellipse with shape parameters $a$ and $b$.}
	\end{figure}

@@

\begin{frame}{MCE}
	\begin{block}{Definition}
		Demand set $\Pp=\{p_1, \dots, p_n\}$;\\
		Weights $\Ww = \{w_1, \dots, w_n\}$;\\
		Shape parameters $\Rr = \{(a_1, b_1), \dots, (a_m, b_m)\}$, $a_j > b_j > 0$.\\
		Set of functions $\E = \{E_1, \dots, E_m\}$, $E_j(q_j)$ is the $j$-th ellipse's coverage region.
	\end{block}
\end{frame}

\begin{frame}[allowframebreaks]
	\frametitle{References}
	\bibliographystyle{amsalpha}
	\bibliography{../references.bib}
\end{frame}

### 2020-03-10 defesa/tex/chapter/introducao.tex
wip

PMCLP under Euclidean distance is also found in the literature as \sigla{MCD}{Maximum Covering by Disks}.
Early works only tackled the one-disk version of it. In \citeonline{chazelle:1986}, a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
The $m$ disks version of MCD was studied in \citeonline{cabello:2006}, which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$. To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
Additionally, in \citeonline{aronov:2008}, one-disk maximum covering is proven to be 3SUM-HARD. This means that maximizing the number of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.

@@

Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:mcd2}, we proposed an algorithm for MCE based on developments we made for a more general version of that problem that considers not only ellipses but any strictly convex disk as facilities;
in \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented; in \autoref{chapter:e3p}, we introduce a new geometry problem, which surged as a subproblem of MCER, and propose an algorithm for it;
in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCER; 
in \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.

>>>>

PMCLP under Euclidean distance is also found in the literature as \sigla{MCD}{Maximum Covering by Disks Problem}.
Early works only tackled the one-disk version of it. In \citeonline{chazelle:1986}, a $\bigO(n^2)$ algorithm, which still stands as the best in terms of run-time complexity, was proposed beating the prior $\bigO(n^2\log{n})$ algorithm created by \citeonline{drezner}.
The $m$ disks version of MCD was studied in \citeonline{cabello:2006}, which had as its most important result a $(1-\epsilon)$-approximation algorithm which runs in $\bigO(n\log{n})$. To achieve its main goal, however, they developed a deterministic $\bigO(n^{2m-1}\log{n})$ algorithm which gets employed into their approximation scheme.
Additionally, in \citeonline{aronov:2008}, one-disk maximum covering is proven to be 3SUM-HARD. This means that maximizing the number of points covered by a disk is as hard as finding three real numbers that sum to zero among $n$ given real numbers.

@@

Our work is structured in the following way: in \autoref{chapter:definitions}, some definitions and results that are used throughout the next chapters are introduced; in \autoref{chapter:mcd2}, we proposed an algorithm for MCE based on developments we made for a more general version of that problem that considers not only ellipses but any strictly convex disk as facilities.
In \autoref{chapter:e3p} and  \autoref{chapter:mcer} the main results of our work are presented: in \autoref{chapter:e3p}, we introduce a new geometry problem, which surged as a subproblem of MCER, and propose an algorithm for it;
in \autoref{chapter:mcer}, we use the algorithm developed in \autoref{chapter:e3p} to propose a new algorithm for MCER.
In \autoref{chapter:numerical}, numerical experiments are analyzed, and implementation details are given; finally, a conclusion is presented \autoref{chapter:future_work}, along with some suggestions of what can be done in future works on this subject.

### 2020-03-10 defesa/tex/chapter/mcd2.tex
wip

For example, the norms $||x||_p=(\sum_{i} |x_i|^p)^{\frac{1}{p}}$, $p\in \mathbb{N}, p>1$ define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a strictly convex normed space $(\R^2,||\cdot||_{a,b})$, such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.

Instead of developing an algorithm for ellipses only, based on the results of \citeonline{bi}, we describe a more general method that only assumes that the facilities have a strictly convex coverage area, and it is possible to determine the intersection between the boundaries of two of them.
We refer to this more general version of MCE as \sigla{MCSCD}{Planar Maximum Covering Location by Strictly Convex Disks}, and instead of having a list of shape parameters, a list of strictly convex norm functions $\F=\{f_1, \dots, f_m\}$ is given, and an instance of MCSCD is defined as the tuple $(\Pp, \Ww, \F)$. Also, we define for MCSCD the set $\E=\{E_1, \dots, E_m\}$, with $E_j\colon \R^2 \to \R^2$ being a function that takes a center where the $j$-th disk is located and returns the unit disk corresponding to the the norm $f_i$.

@@

An instance of the \sigla{MWC}{Maximum Weight Clique} is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$; 
a norm $||\cdot||$, such that $(\R^2, ||\cdot||)$ is a strictly convex normed plane; and a set of weights \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$. 
Then, we define a set of unit disks $\D:=\{D_1, \dots, D_n\}$, with $D_i:=\{x \in \R^2 \colon ||x-p_i|| \le 1\}$ being a unit disk centered at $p_i$; we also denote by $\partial D_i$ as the circle correspondent to the $i$-th unit disk, and that $w_i$ is the weight of $D_i$.
All that being said, we define an instance of MWC as a tuple $(\Pp, \Ww, ||\cdot||)$.

>>>>

For example, the norms $||x||_p=(\sum_{i} |x_i|^p)^{\frac{1}{p}}$, $p\in \mathbb{N}, p>1$, define strictly convex unit disks, while $||\cdot||_1$ and $||\cdot||_{\infty}$ do not.
Given the shape parameters $(a, b)$ of an ellipse, it is possible to define a strictly convex normed space $(\R^2,||\cdot||_{a,b})$ such that the unit circle $\{x \in \R^2\colon ||x||_{a, b} = 1\}$ is the axis-parallel ellipse with shape parameters $(a, b)$ centered at the origin.

Instead of developing an algorithm for ellipses only, based on the results of \citeonline{bi}, we describe a more general method that only assumes that the facilities have a strictly convex coverage area, and it is possible to determine the intersection between the boundaries of two of them.
We refer to this more general version of MCE as \sigla{MCSCD}{Planar Maximum Covering Location by Strictly Convex Disks Problem}, and instead of having a list of shape parameters, a list of strictly convex norm functions $\F=\{f_1, \dots, f_m\}$ is given, and an instance of MCSCD is defined as the tuple $(\Pp, \Ww, \F)$. Also, we define for MCSCD the set $\E=\{E_1, \dots, E_m\}$, with $E_j\colon \R^2 \to \R^2$ being a function that takes a center where the $j$-th disk is located and returns the unit disk corresponding to the the norm $f_i$.

@@

An instance of the MWC is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$; 
a norm $||\cdot||$, such that $(\R^2, ||\cdot||)$ is a strictly convex normed plane; and a set of weights \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$. 
Then, we define a set of unit disks $\D:=\{D_1, \dots, D_n\}$, with $D_i:=\{x \in \R^2 \colon ||x-p_i|| \le 1\}$ being a unit disk centered at $p_i$; we also denote by $\partial D_i$ as the circle correspondent to the $i$-th unit disk, and that $w_i$ is the weight of $D_i$.
All that being said, we define an instance of MWC as a tuple $(\Pp, \Ww, ||\cdot||)$.

### 2020-03-10 defesa/tex/chapter/mcer.tex
wip

	As it was shown on \autoref{chapter:mce}, $X$ is a region that is limited by arcs of ellipses. As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point, creating a vertex. Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.

@@

	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on it. This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
	Moreover, in Section~\ref{section:ellipses_intersection}, we discuss the problem of determining the intersections between two ellipses. This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points. In \autoref{section:ellipses_intersection}, it is shown that this problem has at most two solutions. Therefore, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.

@@

Let $E$ be the coverage region of an ellipse with shape parameters $(a, b)$. We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \tilde{\Phi}_j(u,v)) \in \R^2\times[0, \pi)$, such that, $\{u, v\}\subset \partial E(q, \tilde{\Phi}_j(u,v))$. That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse. This can be done using the results of Section~\ref{section:ellipses_intersection}.

>>>>

	As it was shown in \autoref{chapter:mcd2}, $X$ is a region that is limited by arcs of ellipses. As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point, creating a vertex. Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \partial E_j(q_j', \theta_j)| \ge 2$.

@@

	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on it. This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$. 
	Moreover, in Section~\ref{section:ellipses_intersection2}, we discuss the problem of determining the intersections between two ellipses. This problem is equivalent to the problem of determining every center and angle of rotation that puts two points on an ellipse, which is the problem used in the definition of $S_j^{(2)}$ for every pair of points. In \autoref{section:ellipses_intersection}, it is shown that this problem has at most two solutions. Therefore, we have that $|S_j^{(2)}| \le 2\binom{n}{2}$.

@@

Let $E$ be the coverage region of an ellipse with shape parameters $(a, b)$. We assume that in \autoref{algoritmo:mcer1}, the procedure $e2p(u, v, a, b)$ returns every $(q, \tilde{\Phi}_j(u,v)) \in \R^2\times[0, \pi)$, such that, $\{u, v\}\subset \partial E(q, \tilde{\Phi}_j(u,v))$. That is, this procedure returns every location for the ellipse with shape parameters $(a, b)$, such that its angle of rotation is $\tilde{\Phi}_j(u,v)$, and the points $u$, $v$ are on the ellipse. This can be done using the results of Section~\ref{section:ellipses_intersection2}.
